Selecting and ranking interesting pairs of cyclic temporal granularities

### 2020-12-07 paper/main.Rmd
added picture and caption

Consider two cyclic granularities $C_i$ and $C_j$, such that $C_i$ maps index set to a set $\{A_k \mid k=1,\dots,K\}$ and $C_j$ maps index set to a set $\{B_\ell \mid \ell =1,\dots,L\}$. Here, $A_k$ and $B_\ell$ are the levels/categories corresponding to $C_i$ and $C_j$ respectively. Let $S_{k\ell}$ be a subset of the index set such that for all $s \in S_{k\ell}$, $C_i(s) = A_k$ and $C_j(s) = B_\ell$. There are $KL$ such data subsets, one for each combination of levels ($A_k$, $B_\ell$). Moreover, consider that in the graphical space, $C_i$ is mapped to facets and $C_j$ is mapped to x-axis.

The algorithm employed for computing the distance measure is summarized as follows:

1. Fix harmony pair $(C_i, C_j)$.

2. Fix $k$. Then there are $L$ groups corresponding to level $A_k$ of $C_i$.

3. Compute  $m = \binom{L}{2}$ pairwise distances between distributions of $L$ unordered levels and $m = L-1$ pairwise distances for $L$ ordered categories.

4. Identify maximum within the $m$ computed distances.

<!-- 5. Compute distribution of maximum distance ($M$) by shuffling the data $200$ times and finishing Steps1-4 in each case. Scale $M$ using the mean and sd of the distribution.  -->

5. Use Steps 1-4 to compute maximum distance for $\forall k \in  \{1, 2, \ldots, K\}$.

6. Compute the distance measure MMPD_raw = median $(M_1, M_2, \dots, M_K)$.

@@

A stronger measure "max" is chosen for aggregating x-axis categories compared to "median" for aggregating facet categories as the measure is intended to put more importance in pointing towards distributional differences between x-axis categories than for facet categories.

>>>>

Consider two cyclic granularities $A$ and $B$, such that $A = \{ a_j: j = 1, 2, \dots, J\}$ and $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets. Let the pairwise distances between combinations be denoted as $d_{(j,k), (j', k')} = JSD(a_{j}b_{k}, a_{j'}b_{k'})$. If $b_{k} = b_{k'}$, distances considered are within-facet. Otherwise they are between-facet.

```{r distance-explain, fig.cap = "Mapping to data space to graphic space shown. Cyclic granularity A is mapped to x-axis and B is mapped to facets and the dotted lines represent the distances between different categories. Panel 1) and 2) show the between-facet distances. Panel 3) and 4) are used to illustrate within-facet distances when categories are un-ordered or ordered respectively. When categories are ordered, distances should only be considered for consecutive x-axis categories. Between-facet distances are distances between different facet levels for the same x-axis category, for example, distances between {($a_1$,$b_1$) and ($a_1$, $b_2$)} or {($a_1$,$b_1$) and ($a_1$, $b_3$)}."}
knitr::include_graphics(here::here("paper/Figs/dist_explain.png"))
```

The maximum weighted pairwise distances are defined as:
$$MEPD = max_{j, j', k, k'}(d*_{(j,k), (j', k')})
\forall j, j' \in \{1, 2, \dots, J\}, k, k' \in \{1, 2, \dots, K\}$$
where,

\begin{equation}
d*_{(j,k), (j', k')} =
\begin{cases}
\lambda * d_{(j,k), (j', k')},& \text{if } b_{k} = b_{k'}\\
(1-\lambda) * d_{(j,k), (j', k')},              & \text{otherwise}
\end{cases}
\end{equation}

<!-- _j$ maps index set to a set $\{B_\ell \mid \ell =1,\dots,L\}$. Here, $A_k$ and $B_\ell$ are the levels/categories corresponding to $C_i$ and $C_j$ respectively. Let $S_{k\ell}$ be a subset of the index set such that for all $s \in S_{k\ell}$, $C_i(s) = A_k$ and $C_j(s) = B_\ell$. There are $KL$ such data subsets, one for each combination of levels ($A_k$, $B_\ell$). Moreover, consider that in the graphical space, $C_i$ is mapped to facets and $C_j$ is mapped to x-axis. -->

 <!-- old -->
<!-- Consider two cyclic granularities $C_i$ and $C_j$, such that $C_i$ maps index set to a set $\{A_k \mid k=1,\dots,K\}$ and $C_j$ maps index set to a set $\{B_\ell \mid \ell =1,\dots,L\}$. Here, $A_k$ and $B_\ell$ are the levels/categories corresponding to $C_i$ and $C_j$ respectively. Let $S_{k\ell}$ be a subset of the index set such that for all $s \in S_{k\ell}$, $C_i(s) = A_k$ and $C_j(s) = B_\ell$. There are $KL$ such data subsets, one for each combination of levels ($A_k$, $B_\ell$). Moreover, consider that in the graphical space, $C_i$ is mapped to facets and $C_j$ is mapped to x-axis.  -->

<!-- The algorithm employed for computing the distance measure is summarized as follows: -->

<!-- 1. Fix harmony pair $(C_i, C_j)$. -->

<!-- 2. Fix $k$. Then there are $L$ groups corresponding to level $A_k$ of $C_i$. -->

<!-- 3. Compute  $m = \binom{L}{2}$ pairwise distances between distributions of $L$ unordered levels and $m = L-1$ pairwise distances for $L$ ordered categories. -->

<!-- 4. Identify maximum within the $m$ computed distances. -->

<!-- <!-- 5. Compute distribution of maximum distance ($M$) by shuffling the data $200$ times and finishing Steps1-4 in each case. Scale $M$ using the mean and sd of the distribution.  --> -->

<!-- 5. Use Steps 1-4 to compute maximum distance for $\forall k \in  \{1, 2, \ldots, K\}$. -->

<!-- 6. Compute the distance measure MMPD_raw = median $(M_1, M_2, \dots, M_K)$. -->

@@

<!-- A stronger measure "max" is chosen for aggregating x-axis categories compared to "median" for aggregating facet categories as the measure is intended to put more importance in pointing towards distributional differences between x-axis categories than for facet categories. -->
